Incentivizing Exploration with Unbiased History

### 2018-10-24 2level.tex
update 2-level figure

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \filldraw[fill=blue!20!white]
 (0,2)--(10,2)--(10,3)--(0,3)--cycle;
  \filldraw[fill=red!20!white]
  (0,0)--(1,0)--(1,1)--(0,1)--cycle;
  \draw[dashed] (0.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (1,0)--(2,0)--(2,1)--(1,1)--cycle;
  \draw[dashed] (1.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (2,0)--(3,0)--(3,1)--(2,1)--cycle;
  \draw[dashed] (2.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (3,0)--(4,0)--(4,1)--(3,1)--cycle;
  \draw[dashed] (3.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (9,0)--(10,0)--(10,1)--(9,1)--cycle;
  \draw[dashed] (9.5,1)--(5,2);
  \node at(5,0.5){$\cdots$};
  \node at(6,0.5){$\cdots$};
  \node at(7,0.5){$\cdots$};
  \node at(8,0.5){$\cdots$};
  \node at(5,2.5){$T -T_1 \cdot \GdT$};
  \node at(0.5,0.5){$\GdT$};
  \node at(1.5,0.5){$\GdT$};
  \node at(2.5,0.5){$\GdT$};
  \node at(3.5,0.5){$\GdT$};
  \node at(9.5,0.5){$\GdT$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \draw[->] (11,0)--(11,3);
  \node at(11.5,1.5)[ rotate=90]{Time};
\end{tikzpicture}

\caption{Structure of information graph for the 2-level policy. Each
  red ``box'' is level 1 corresponds to a path connecting a set of
  $T_G$ agents. The entire history in level 1 is then aggregated and
  shown to each agent in level 2.}
\label{fig:2level}
\end{figure}

>>>>

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \filldraw[fill=blue!20!white]
 (0,2)--(10,2)--(10,3)--(0,3)--cycle;
  \filldraw[fill=red!20!white]
  (0,0)--(1,0)--(1,1)--(0,1)--cycle;
  \draw[dashed] (0.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (1,0)--(2,0)--(2,1)--(1,1)--cycle;
  \draw[dashed] (1.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (2,0)--(3,0)--(3,1)--(2,1)--cycle;
  \draw[dashed] (2.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (3,0)--(4,0)--(4,1)--(3,1)--cycle;
  \draw[dashed] (3.5,1)--(5,2);
  \filldraw[fill=red!20!white]
  (9,0)--(10,0)--(10,1)--(9,1)--cycle;
  \draw[dashed] (9.5,1)--(5,2);
  \node at(5,0.5){$\cdots$};
  \node at(6,0.5){$\cdots$};
  \node at(7,0.5){$\cdots$};
  \node at(8,0.5){$\cdots$};
  \node at(5,2.5){$T -T_1 \cdot \GdT$};
  \node at(0.5,0.5){$\GdT$};
  \node at(1.5,0.5){$\GdT$};
  \node at(2.5,0.5){$\GdT$};
  \node at(3.5,0.5){$\GdT$};
  \node at(9.5,0.5){$\GdT$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \draw[->] (11,0)--(11,3);
  \node at(11.5,1.5)[ rotate=90]{Time};

  \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=0pt] (10,-0.2) -- (0,-0.2) node [black,midway,yshift=-0.6cm] {$T_1$ runs of \ALGG in parallel};
\end{tikzpicture}

\caption{Structure of information graph for the 2-level policy. Each
  red ``box'' in level 1 corresponds to a path connecting a set of
  $T_G$ agents. The entire history in level 1 is then aggregated and
  shown to each agent in level 2.}
\label{fig:2level}
\end{figure}
